EpisoPass: Password Management based on Episodic Memories

### 2016-08-29 paper/Password2016/paper.tex
Joannaによる添削を入れたもの

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{marginnote}

@@

Since passwords are difficult to handle, various other authentication methods have been proposed.
For example, image-based authentication\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
biometrics authentication\footnote{
  % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
  % \url{https://en.wikipedia.org/wiki/Biometrics}
  \url{https://en.wikipedia.org/w/index.php?title=Biometrics&oldid=736189000}
},
behavior-based authentication\cite{Dandapat:2015:AYD:2702123.2702457}, and many others.

@@

However, password-based authentication is still the most
convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.

Given we will have to continue to live with password-based
authentication systems for the foreseeable future, we have to devise
practical methods for handling many passwords, and various ``password
managers''
have been proposed\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
%
Password managers remember users' passwords and aim to directly enter
them into the login pages of the various services a user wants to
access.
%
The burden on the user is reduced by requiring just a single ``master
password'' to access the database of stored passwords.
%
Although password managers are widely used and a clear step forward
from having to remember multiple passwords, uses nonetheless have to
remember the master password or use a special hardware device for
safely handling the password database, and password managers usually
run on only a limited set of devices.

@@

If we want to avoid having to carry any special device for
authentication, either we must used some form of biometrics, or all
the information required for the authentication must be must be stored
in the user's memory.
%
However, the biggest problem with memory-based authentication is that
users cannot reliably remember passwords or master password that are
long and complex enough to be secure.

For this reason, we believe that it is far better to ``generate''
something for the authentication, based on a user's episodic
memories. This has the benefit that unlike a password, a person is
highly unlikely to forget such episodic memories.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We therefore propose \textit{EpisoPass}, a password manager that
generates strong passwords based only on a user's secret and
unforgettable episodic memories.

@@

The idea of using episodic memories for authentication has a long history.
Early papers suggested using episodic memories for creating passwords.
Authentication by using secret questions,
sometimes called as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538},
has long been used as an
alternative to password-based authentication systems.
%
% However, conversion from episodic memories to password strings
% was not studied at all.

@@

\begin{enumerate}
\item A user registers many question texts related to the user's personal
secret episodic memories that the user never forgets,
and provides a correct answer and additional fake answers.

@@

\item EpisoPass shows the data to the user so that
the user can select the right answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates
strong password candidate strings.
After selecting all the right answers,
the user copies the calculated string
and register it as the password for the service.
\end{enumerate}

\begin{figure}[H]
\centering
% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
\caption{Generating an Amazon password with EpisoPass.}
\label{web1}
\end{figure}

\subsection{Using EpisoPass on a browser}

Figure \ref{web1} shows how to generate a password
on EpisoPass running on a browser.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for each question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections.
When the user selects the correct answers to all the questions,
the right password is calculated and shown at the top.

@@

In Figure \ref{web1},
``\textsf{Amazon123456}'' is provided as the seed string,
and according to the selections to the five questions,
the seed string is converted to a string
``\textsf{Tblgeq808187}'',
which can be used as the password for Amazon.com.

When the user clicks another candidate,
the seed string is converted to another strings like
``\textsf{Xvdkzb940345}'' (Figure \ref{web11}).

\begin{figure}[H]
\centering
\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
\caption{Selecting a different answer.}
\label{web11}
\end{figure}

In this way, different selections yields different password strings and
the password string generated after selecting correct answers can be
used as the password for the service.

Capital letters in the seed string are substituted to capital letters in the password,
and digits in the seed string are substituted to digits,
so that generated passwords conforms to password character restrictions
sometimes requested by the service.

The first question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the question with a photo at the bottom is related to a more recent event
which the author believes he will never forget.
All the questions are based on the author's episodic memories
that he thinks he never forgets, and he believes that
nobody else knows which one of the candidate is the right answer.

Questions and answers can be edited directly on the browser, and they can be
saved on the server by clicking the ``save to server'' button.
The Q-A data sets are saved on the server,
but no information about the correct answer or the
generated password is saved on the server.
The Q-A data in JSON format can be downloaded to the local machine
by clicking the ``save to file'' button.
the data can be uploaded to the server by dragging the JSON file to the EpisoPass page.

When we change the secret string to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Onjbrppy030937}'',
as shown in Figure \ref{web2}.
In this way, we can generate different passwords for
different services just by changing the seed string.

\begin{figure}[H]
  \centering
%  \includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
  \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
  \caption{Generating the password for Facebook.}
  \label{web2}
\end{figure}

Character substitution is performed based on the hash value
calculated from concatenating all the questions and selected answers.
%
For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
to the question ``\textbf{\texttt{Who's the bully?}}'',
a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for calculating the hash value.

The last question in Figure \ref{web1} is not a secret question, but a question
for generating different passwords for different situations.
By providing such a question, users can generate completely different passwords
for different months and years, for example.

@@

If a user doesn't like to use the EpisoPass service on the Net,
he can use an EpisoPass application on Android
which does not use network connections.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
by clicking the ``Android app'' button at the top.
The application contains all the information required for generating passwords.
(The application is compiled and built on the server.)

When the user runs the application and selects the correct answer
to each question, he can eventually get the password and copy it to the password entry.
(Figure \ref{android1},\ref{android2})

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
\caption{Running EpisoPass on Android.}
\label{android1}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.7\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
\caption{After finishing selections.}
\label{android2}
\end{figure}

The calculation is performed on Android without network connection,
and the user can safely generate passwords 
without feeling the fear of being observed by attackers.

@@

When a user use the EpisoPass service or the EpisoPass application,
he has to type or copy the password string after generating the password.
Since it is not convenient,
we provide a browser extension for using EpisoPass on the login window of
various Web services.

A browser extension is a JavaScript add-on program which runs
on top of existing Web pages.
%
Figure \ref{extension} shows the login page of Amazon.com, with which
EpisoPass questions are automatically displayed by the browser extension.
%
Here, when the Amazon login page is accessed from the browser,
the browser extension program automatically runs on the page,
acquires questions and answers from the EpisoPass server,
and shows them to the user just the same way as the Android application.
%
After answering all the questions, a password is calculated from the
selected answers and pasted to the password field of the page.
Using the extension, users can login to various services just by
answering questions, without seeing any password string.
It looks as if these services are offering
EpisoPass-based authentication.

\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
\caption{Using EpisoPass on the login window.}
\label{extension}
\end{figure}

\section{Discussions}

In this section, we discuss the advantages and caveats of using EpisoPass.

@@

The biggest advantage of using EpisoPass is that
users don't have to remember strong password strings.
%
Users of EpisoPass can save the seed string and question-answer data
at any place, and easily generate passwords by running
EpisoPass and answering questions.
If the question is based on old unforgettable episodic memories,
there is little chance of losing passwords
as long as the seed string and the questions are available.
If the user's memory is related to an episode of 20 years ago and the user clearly
remembers the episode now, it is unlikely that he forgets the episode 10 years later.

@@

In the previous examples showing the author's EpisoPass questions,
a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.
Such strings are used because they are easily memorable.
Of course any seed string can be used as seeds for various services,
and automatic generation of seed strings is possible.

% although generating service-specific unique seed string is not trivial.
% For example, users can use the same username and password both
% for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.

@@

The strength of the generated password depends on the number of
questions and the secret level of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}%
\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but the strength of secret questions has not been studied enough.
%
When we use 10 secret questions with 20 answers and
there's no clue for the answer,
1 billion ($20^{10}$) trials should be performed to check
all the combinations of the answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks\cite{Florencio:2007:SWP:1361419.1361429}.

@@

Questions such as ``Which food do you like best?'' should be avoided,
since friends or family might know the user's tastes, thereby allowing 
others to select the correct answer.

Questions related to an episode which the user is proud of should also be
avoided, since this is a something the user might prefer to discuss with others.
We don't usually talk about trivial bad experiences with other people,
but we might boast about good experiences (some might even write blog posts about them).
Similarly our tastes ({\it e.g.\/} favorite foods) might change in the long run.
Using such episodes for questions should therefore be avoided.

@@

It can be difficult to provide a large number of false answers to a question like
``what is your favorite sport?''
because the number of possible answers is limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is straightforward.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.

In this way, false answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks%
\cite{Huang:2012:LFC:2426725.2426728,BooWa,Wang:2007:LSE:1441428.1442086}. % Boo!Wa!
We can use such systems to provide a list of potential false answers almost automatically.

@@

Users don't have to be very careful about handling questions and answers.
They can even be put on a public place
if enough amount of questions and fake answers are provided.
%
Keeping secrets is always a pain for many people including
the authors, but if the whole questions and answers used on EpisoPass
can be put on a public place,
handling it becomes very easy.
Usually we have to be very careful about handling
secret information like passwords, secret key for SSH, etc.
because they should not be copied or saved at unsafe places.
On the other hand,
we can save the EpisoPass data as a plain text file and put it at
any place without great care, since malicious person cannot calculate
passwords without having the owner's episodic memories.

@@

\subsection{Risk of password leak at the service side}

If one of the passwords generated by EpisoPass is revealed
for some reason, other passwords based on the same questions
might also be revealed.
%
For example, if Twitter is attacked by a cracker and
the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
is revealed to the attacker,
the attacker can try all the answer combinations and find out
the answers to all the questions,
if questions and answers are also known by the attacker.
Once all the answers to the questions are known,
the attacker can freely generate all the passwords
generated with the same questions.

To prevent such trouble, it is safer to keep all the questions and answers
in a secret place or
use sufficient number of questions so that brute-force does not work.

@@

Old pictures can be used as the questions of EpisoPass,
just like the question shown at the bottom of Figure \ref{web1}.
Even when people cannot create good secret questions,
people can fairly easily select a secret image from their photo collections
and use it as the question.
For example, if you have an old picture of your friend,
you can use it as the question
and use his real name as well as other similar fake names.

% 画像検索とかされないようにする必要はある

Of course, the photo should not have information related to the
person's real name, since image search is fairly easy on the Web these days.

@@

As shown in previous sections,
there have been many attempts for replacing password-based authentication systems,
but none of them are found to be better than
password-based systems\cite{Bonneau:ReplacePasswords}.
%
Although cognitive password systems have been studied for a
long time\cite{Lazar2011}\cite{Zviran:1990:UAC:100512.100538},
they were implemented as a replacement to password-based systems,
and no password-generation system have been proposed
based on cognitive authentication.

@@

The idea of using episodic memories for authentication is not new.
In fact, using episodic memories for selecting password
has generally been recommended,
and many current computer users are probably using password that are
in some way related to their episodic memories.

Recently, people are trying to use mobile devices for authentication,
because mobile devices remember all the user's behaviors and
the user can easily recall what he did%
\cite{Dandapat:2015:AYD:2702123.2702457}%
\cite{Das:2013:ECE:2493432.2493453}%
\cite{GuptaWRLGB12}%
.
For example, if a user can answer questions like
``who did you call last night?'' correctly, the authentication will succeed.
Using mobile or wearable devices for authentication will become more usable
in the future,
but users should have a fairly good long-term memory about their behaviors,
and that not easy for everybody.

Various types of image-based authentication systems have been proposed recently%
\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords},
in the hope that images are easier to remember than text
because images are usually more directly linked to episodic memories.
However, on many systems,
users have to remember new information related to the images
used in the authentication process, or
perform special operations on the image, and
it is not much easier than remembering passwords.
%
Image-based authentication based on episodic memories might work
if anyone can prepare many images 
that are tightly linked to his episodic memories.
However, finding such images is usually not easy, and
image-only authentication systems would not take off
until simple and effective technique is invented.

Even when a new ideal authentication method is invented,
replacing all the password-based systems should take very long, and
various password managers should be used until the ideal method
prevails in the world.
In the age of password-based authentication,
using password managers seems to be the only way to tackle
the problem of passwords.
%
While most of the password managers only remember passwords given by the user,
generating passwords with a password manager is a new approach for
handling password-based systems.
Just like EpisoPass generates passwords,
Versipass\cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
helps the user to generate password strings
using ``visual cues'' on an arbitrary image.
Instead of directly using images for authentication,
users use the system to generate a password text with the help of
the image shown to the user.

@@

EpisoPass has been used by the authors for more than three years, and
the authors are using it for various services including
Twitter, Facebook, Amazon, Skype, etc.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, taking care of many passwords was really
a pain for the authors, but
currently all the information for generating passwords is put on the cloud
and no trouble has been found during the period.
%
After the introduction of browser extension,
logging into various services became even easier,
because visiting the EpisoPass service is unneccesary.

EpisoPass service have been on the Web and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}, but
unfortunately EpisoPass is currently not used by many people.
One big reason is that most people cannot fully understand the
idea of EpisoPass and also cannot fully trust it
because it is not operated by a big IT company.
% nor supported by famous computer users.
Another reason might be that users cannot estimate the strength
of EpisoPass.
Since all the questions and answers are
quite obvious to the users,
they might feel that everyone else also know the episode
and easily solve all the questions.
These kinds of psychological issues are quite important for
an authentication system for everybody,
and we hope to eliminate such obstacles in the future.

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{marginnote}

@@

Since passwords are difficult to handle, various other authentication methods have been proposed.
For example, image-based authentication \cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords}, 
biometrics\footnote{
  % \textsf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Biometrics}
  \url{https://en.wikipedia.org/w/index.php?title=Biometrics&oldid=736189000}
},
behavior-based authentication \cite{Dandapat:2015:AYD:2702123.2702457}, and many others.

@@

% \marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
However, password-based authentication is still the most
convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.

Given we will have to continue to live with password-based authentication systems for the foreseeable future,
we have to devise practical methods for handling many passwords, and various ``password managers'' have been proposed
\cite{OnePassword,Dashlane,MilPass,LastPass,KeyPass,NortonIDSafe,IDManager}.
%
Password managers remember users' passwords and aim to directly enter them into the login pages of the various services a user wants to access.
%
The burden on the user is reduced by requiring just a single ``master password'' to access the database of stored passwords.
%
Although password managers are widely used and a clear step forward from having to remember multiple passwords, uses nonetheless have to remember the master password or use a special hardware device for safely handling the password database, and password managers usually run on only a limited set of devices.

@@

If we want to avoid having to carry any special device for authentication,
either we must used some form of biometrics, or all the information required 
for the authentication must be
must be stored in the user's memory.
%
However, the biggest problem with memory-based authentication is that
users cannot reliably remember passwords or master password that are long and complex enough to be secure.
For this reason, we believe that
it is far better to ``generate'' something for the authentication,
based on a user's episodic memories. This has the benefit that unlike a password, a person is highly unlikely to forget such episodic memories.
%
% We believe that a password manager should have the following features.
% (1) It should be available on any platform including PCs, smartphones, and the Web.
% (2) Users should not have secret information (e.g. master password) or special device.
% (3) Rely only on the information in the user's brain.
%
We therefore propose \textit{EpisoPass}, a password manager that generates strong passwords
based only on a user's secret and unforgettable episodic memories.

@@

\begin{figure}
\centering
% \includegraphics[width=1.0\columnwidth]{figures/c1bd6e7f67698c70978f528ccd2339d9}
\includegraphics[width=1.0\columnwidth]{figures/4d13e6804ba790624c1f8e2b8255bde5}
\caption{Generating an Amazon password with EpisoPass.}
\label{web1}
\end{figure}

% \marginnote{You mention that episodic memories and cognitive passwords
%   have been used in the past, but it's not clear to me (from the text
%   here) why your system is different. Perhaps you could put a sentence
%   or two about this?}

The idea of using episodic memories for authentication has a long
history and early papers suggested using episodic memories for
creating passwords. Authentication using secret questions is sometimes
referred to as ``cognitive
passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches
have been used as an alternative to password-based authentication
systems.
%
While cognitive passwords were aimed to be alternatives to
password-based systems, EpisoPass is a system for supporting
password-based systems using episodic memories.

@@

\begin{enumerate}
\item A user registers multiple question texts related to their own personal
secret unforgettable episodic memories. For each question they must provides
a single correct answer and multiple additional incorrect answers.

@@

\item EpisoPass shows the questions and answers to the user allowing
them to select the correct answer for each question.
Based on the user's selections,
EpisoPass substitutes characters in the seed string and generates a
strong password candidate string.
After selecting all of the correct answers,
the user copies the calculated string
and registers it as the password for the service.
\end{enumerate}

\subsection{Using EpisoPass in a browser}

Figure \ref{web1} shows how to generate a password
on EpisoPass running in a browser by accessing the EpisoPass site.
Many questions related to the user's episodic memories are shown to the user,
and many candidate answers are also shown for each question.
When a user clicks and selects one of the answers for a question,
the seed string shown at the top-left is converted to a
candidate password string based on the selections. If incorrect answers are chosen the wrong password will be generated. On the other hand, when the user selects the correct answers for all of the questions,
the correct password is calculated and shown at the top of the page.

@@

In Figure \ref{web1},
``\textsf{Amazon123456}'' is provided as the seed string,
and based on the selections to the ten questions,
the seed string is converted to the string
``\textsf{Tblgeq808187}'',
to be used as the password for Amazon.com.

When the user clicks on different candidate answers 
the seed string is converted to a completely different strings, such as
``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.

In this way, different selections yield different password strings and
the unique password string generated after selecting the correct answers should be
used as the password for the service.

Capital letters in the seed string are substituted for capital letters in the password,
and digits in the seed string are substituted for digits. In this way
the generated password can be arranged to conform with any password character restrictions
the site might impose.

The first question in Figure \ref{web1}
is based on the author's episodic memory at elementary school,
and the question with a photo at the bottom is related to a more recent event
which the author believes he will never forget.
All the questions are based on the author's episodic memories that he's unlikely to ever forget,
and that he believes nobody else will know the correct answer for.

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{figures/8447eaba1ede0f678b3ce6fea63681f3}
\caption{Selecting a different set of answers.}
\label{web11}
\end{figure}

Usability has been considered as a key consideration, and the questions 
and answers in the figures can be edited directly in the browser. They can be
saved on the server by clicking the ``save to server'' button or saved locally
if the user prefers.
While the Q-A data sets are saved, no information about the correct answer or the
generated password is saved on the server. Consequently there is no requirement for the user
to trust the server to keep the data secret.
The Q-A data can be downloaded to the user's local machine in JSON format 
by clicking the ``save to file'' button. To upload the data back to the server, the user
simply drags the JSON file to the EpisoPass page.

When the secret string is changed to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Onjbrppy030937}'',
as shown in Figure \ref{web2}.
In this way, the user can generate different passwords for
different services just by changing the seed string.

\begin{figure}
  \centering
%  \includegraphics[width=1.0\columnwidth]{figures/0e2820c279afc70520482e0fc53b6ed9}
  \includegraphics[width=1.0\columnwidth]{figures/ab4517dd593c1cabab5fecef546f7e88}
  \caption{Generating a new password for Facebook.}
  \label{web2}
\end{figure}

Character substitution is performed based on the value
calculated by hashing a concatenation of all the questions and selected answers.
%
For example, if the user selects ``\textbf{\texttt{Ebisawa}}''
as the answer to the question ``\textbf{\texttt{Who's the bully?}}'',
a string including ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for calculating the hash value.

The last question in Figure \ref{web1} is not intended as a secret question based on an
episodic memory, but is instead a question
for generating different passwords for different situations.
By providing a question like this, the user can generate completely different passwords
for different months and years, say.

@@

% \marginnote{Is the Android app generated as a unique app for each
%  user? If so, I think it's worth making this clear.}

If a user prefers not to use the EpisoPass service on the Web, there
is an alternative EpisoPass application for Android which requires no
network connection.  After registering questions and answers on the
EpisoPass service, the user can download an Android application from
the server by clicking the ``Android app'' button at the top of the
page.  The application unique to the user is compiled and built on the
server and contains all of the information needed for the particular
user to generate passwords using the Q-A sets entered.

When the user runs the application and selects the correct answer
to each question, the password will be generated in the same way as
on the site, as shown in Figures \ref{android1} and \ref{android2}.
This can then be copied to the password entry for access
to a particular service.

\begin{figure}
\centering
\includegraphics[width=0.4\columnwidth]{figures/429eec261024dc6c85351f51c12f09b4}
\caption{Running EpisoPass on Android.}
\label{android1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.4\columnwidth]{figures/ba8f5aeaa935ad63437969f4d746746b}
\caption{After finishing selections.}
\label{android2}
\end{figure}

The calculation is performed on Android without the need for a network connection,
so the user can safely generate passwords without being concerned about an
attacker observing any data transfer.

@@

One of the difficulties of the previous two approaches is that the user 
must re-type or copy the password string into the service's password
field after it's been generated.
This isn't ideally convenient, so we have also developed a browser 
extension that allows EpisoPass to be used directly with the login
page of services on the Web.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{figures/aeff16ffcab956e554364e9e5aca8359}
\caption{Using EpisoPass on the login window.}
\label{extension}
\end{figure}

A browser extension is a JavaScript add-on program which runs
on top of existing Web pages.
%
Figure \ref{extension} shows the login page of Amazon.com, with the 
EpisoPass questions automatically overlaid directly onto the page
by the browser extension.
%
When the user accesses the Amazon login page,
the browser extension automatically runs on the page,
acquires the questions and answers from the EpisoPass server,
and displays them using the same style as for the Android application.
%
After answering all of the questions, a password is calculated from the
selected answers and automatically pasted into the password field of the page
by the extension. In this way users can log in to various services just by
answering the questions presented, and without even seeing the password string.
It appears as if the EpisoPass-based authentication is being provided directly
by the services themselves.

\section{Discussion}

In this section, we discuss the advantages and potential disadvantages of using EpisoPass.

@@

% \marginnote{The fact that an `old' memory is unlikely to be forgotten
%   is perhaps obvious, but this could be a good place to cite a paper
%   on memory/psychology about this if you're aware of any?}

The biggest advantage of using EpisoPass is that
users don't have to remember strong password strings.
%
The seed string and question-answer data is essentially public,
and users of EpisoPass can save them wherever is convenient. They can
then easily generate passwords by running
EpisoPass and answering the questions.
If a question is based on old unforgettable episodic memory,
there is little chance of losing the password for a service
as long as the seed string and questions are available.
If the user's memory is related to an episode that took place 20 years ago, say, and the user clearly
still remembers the episode now, it is unlikely the episode will be forgotten in the future.

@@

% \marginnote{In the comments you mention that ``generating
%   service-specific unique seed string is not trivial''. I think this
%   is worth mentioning in the paper.}

In the previous examples showing the author's EpisoPass questions, a
seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.  Such strings were
chosen because they are easily memorable.  In practice any seed string
could be used as the seeds for the various services, and automatic
generation of seed strings is a possibility, although generating
service-specific unique seed string is not trivial.  For example,
users can use the same username and password both for Amazon.com and
Amazon.co.uk, but not for Amazon.co.jp.

@@

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
% considerably more than a billion (closer to 10 thousand billion,
% (US) or 10 million million (UK).}
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

@@

Questions such as ``Which food do you like best?'' should be avoided,
since friends or family might know the user's tastes, thereby allowing 
others to select the correct answer.
Questions related to an episode which the user is proud of should also be
avoided, since this is a something the user might prefer to discuss with others.

We don't usually talk about trivial bad experiences with other people,
but we might boast about good experiences (some might even write blog posts about them).
Similarly our tastes ({\it e.g.\/} favorite foods) might change in the long run.
Using such episodes for questions should therefore be avoided.

@@

It can be difficult to provide a large number of false answers to a question like
``what is your favorite sport?''
because the number of possible answers is limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is straightforward.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.
because we can use the list of states in the U.S. as possible answers.

In this way, false answers can be easily generated
if it is possible to collect words which belong to the same
category as the right answer.
%
Various methods have been proposed for collecting words in the
same category, mainly for information retrieval tasks
\cite{Huang:2012:LFC:2426725.2426728,BooWa,Wang:2007:LSE:1441428.1442086}. % Boo!Wa!
We can use such systems to provide a list of potential false answers almost automatically.

@@

Users don't have to be very careful about handling questions and answers.
They can even be stored in a public place
given a sufficient number of questions and fake answers are provided.
%
Keeping secrets is a considerable effort for most people (including
the authors), but if the entire set of questions and answers used for EpisoPass
can stored publicly,
handling it becomes straightforward.
This is in contrast to the care needed when handling 
secrets like passwords, secret keys for SSH, {\it etc}. which should
never be copied to or saved in an unsafe place.
The EpisoPass data can be stored as a plain text file wherever is convenient
for the user, since a malicious attacker isn't able to generate
a valid password without also knowing the owner's relevant episodic memories.

@@

\subsection{Risk of server-side password leaks}

If one of the passwords generated by EpisoPass were to be revealed
for some reason, there is a danger that other passwords based on the same questions
might also be revealed.
%
For example, if Twitter is attacked by a hacker and
the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
is revealed to the attacker,
the attacker could test all answer combinations. If the attacker also had access
to the question and answer strings used, they could then establish the correct 
answers used to generate the password.
Once all the answers to the questions are known,
the attacker can then freely generate all of the user's passwords
generated from the same set of questions.

% \marginnote{It may be helpful to give an indication of how many Q-A sets you think
% would be considered `sufficient' here.}
%
To prevent this, it is safer to keep all of the questions and answers
in a secret place or
use sufficient questions to prevent such a brute-force attack from being viable.

@@

% \marginnote{The use of images is nice, but I don't find your argument
%   so convincing here. I have two concerns: first the claim that
%   selecting images will be easy. Second, the example you provide
%   doesn't seem strong, since other people are likely to be able to
%   identify a friend from a photograph.}

Pictures can also be used as EpisoPass questions,
similar to that shown at the bottom of Figure \ref{web1}.
Even if people find it difficult to create good secret questions,
selecting an image from their photo collections
and using it as the question should be straightforward.
For example, if you have an old special picture of a place you visited,
you can use it as the question and use the name of the place
as well as other similar fake place names.
For a secret question, a low-quality photo is better than a
high-quality photo because a low-quality photo
like the one shown in Figure \ref{web1} are not
easily recognizable by other people.

Of course, it's important the photo should have no information related
to the location, especially given how sophisticated
Web-based image searching has become.

@@

As discussed in previous sections,
there have been many attempts to replace password-based authentication systems,
but none of them have yet become as widely deployed as
passwords \cite{Bonneau:ReplacePasswords}.
%
Although cognitive password systems have been an area of study for 
many years \cite{Lazar2011,Zviran:1990:UAC:100512.100538},
implementations up to now have all been intended as replacements 
to password-based systems, requiring support from the services involved.
As far as the authors are aware, ours is the first password-generation systems to be
based on cognitive authentication.

@@

The idea of using episodic memories for authentication is also not new.
In fact, using episodic memories for selecting passwords
has generally been recommended,
and many current computer users are probably using password that are
in some way informally related to their episodic memories.

Recent work has considered the use of mobile devices for authentication,
in particular harnessing the fact that a mobile device captures large quantities
of personal information. A mobile device may therefore be able to identify
its user based on their previous behavior; events which only the user would be able to recall \cite{Dandapat:2015:AYD:2702123.2702457,Das:2013:ECE:2493432.2493453,GuptaWRLGB12}%
.
For example, if a user can answer questions such as
``who did you call last night?'' correctly, the authentication will succeed.
Using mobile or wearable devices for authentication will become more usable
in the future,
but in order for this to work effectively users must be able to remember potentially
arbitrary behavior over the long-term. This may be a challenge for many people, and the 
benefit of EpisoPass in comparison is that the user is able to select memories that they
know to be memorable, rather than having their mobile device choose them arbitrarily.

Various types of image-based authentication systems have been proposed recently%
\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
based on the realisation that images are easier to remember than text
given they are usually more directly linked to episodic memories.
However, some image-based authentication systems request
users to remember new secrets related to the images instead of
using the users' old episodic memories.
This turns out to be not much easier to remember than passwords.
%
% \marginnote{This statement seems to contradict what you said above
%   about it being easy to find images. Probably the phrasing just needs
%   a bit of refinement.}

Image-based authentication based on episodic memories might work
if users can prepare many images 
that are tightly linked to their episodic memories.
However, finding such images is usually not straightforward, and
image-only authentication systems are unlikely to become popular
until simple and effective techniques for doing so have been developed.

Even when a new ideal authentication method is invented,
replacing all the password-based systems will still be a lengthy process. 
Password managers will therefore remain important until this hypothetical
ideal solution has become ubiquitous.
In the age of password-based authentication,
using password managers seems to be the only way to tackle
the problem of passwords.
%
While most of the password managers only remember passwords given by the user,
generating passwords with a password manager is a new approach for
handling password-based systems.
Just like EpisoPass generates passwords,
Versipass \cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
helps the user to generate password strings
using ``visual cues'' from an arbitrary image.
Instead of directly using images for authentication,
users use the system to generate a password string with the help of
the image shown to the user.

@@

EpisoPass has been used by the authors for more than three years
for various services including Twitter, Facebook, Amazon, Skype, {\it etc}.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, managing multiple passwords was a significant challenge
for the authors. We now have all the information for generating passwords 
stored in the cloud and no problems have arisen from this during this period.
%
Since the introduction of our browser extension, visiting the EpisoPass 
service has now become unnecessary, making authentication to the various
services even easier.

The EpisoPass service is available via the Website and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}. EpisoPass currently has only a small user-base, one major
reason being that most people cannot fully understand the
idea behind EpisoPass, and may not trust it without the 
support of a well-known IT company.
% nor supported by famous computer users.
Another reason is that it's difficult for general users to 
assess the security of EpisoPass.
Since the intention is for the questions and answers to be obvious
to those that know them (but not to others), users may lack
confidence in their answers being unknown to others.
Any authentication system expecting widespread use must take
such psychological issues seriously, and we hope to address 
such issues in future work.
